The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-11-13 Manuscript_draft/Draft.Rmd
Hypotheses

Here, we hypothesized that:
(1) logging of trees will decrease the respiration rates because of the strong decrease in vegetation activity and microbiota associated. In turn, addition of slash will provide labile organic matter to decompose increasing the respiration rates. 
(2) the variation in soil respiration would be mainly dependent on microclimatic variables (soil temperature and moisture), especially in the management treatments where vegetation was removed, since heterotrophic respiration will prevail over autotrophic respiration, and where the litter layer (slash) was removed
(3) the sensitivity of soil respiration to microclimatic conditions will also depend on the type of climate/forest, being the Mediterranean the less sensitive as the microbial communities will be better adapted to the strong seasonal changes in water availability.
(4) the sensitivity of respiration to microclimate will decrease as the time passes since the disturbance because of new fresh C input from the growth of understory vegetation

To test these hypotheses, we have recorded data on soil respiration and microclimate every month in three replicated Quercus forests across Europe subjected to different forest management strategies during three years. We have analysed the sensitivity of soil respiration to microclimate (i.e., soil temperature and soil moisture) by constructing a mechanistic parametric model and compared to a non-parametric model (i.e., random forest). We have also explored the main drivers of variation in Q10 across different forests and forest managements disturbances.
# Material and methods

>>>>

Here, we hypothesized that:
(1) logging of trees will decrease the respiration rates because of the strong decrease in vegetation activity and microbiota associated. This decrease will be compensated by addition of slash which provides labile organic matter, increasing the heterotrophic respiration. 
(2) soil respiration would be more dependent on microclimatic variables (soil temperature and moisture), in the management disturbance treatments where the vegetation was removed and where the litter layer (slash) was removed, by depletion of labile organic matter. Likewise, the sensitivity of respiration to microclimate will decrease as the time passes since the disturbance because of new fresh C input from the growth of understory vegetation
(4) the sensitivity of soil respiration to microclimatic conditions will also depend on the type of climate/forest, being the Mediterranean the less sensitive as the microbial communities will be better adapted to the strong seasonal changes in water availability.

To test these hypotheses, we have recorded data on soil respiration and microclimate every month in three replicated Quercus forests across Europe subjected to different forest management strategies during three years. We have analysed the sensitivity of soil respiration to microclimate (i.e., soil temperature and soil moisture) by constructing a mechanistic parametric model and compared to a non-parametric model (i.e., random forest). We have also explored the main drivers of variation in Q10 across different forests and forest managements disturbances.

# Material and methods
